skater: An R package for SNP-based Kinship Analysis, Testing, and Evaluation

### 2021-07-15 paper/paper.Rmd
typo

author:
  - name: Stephen D. Turner
    affiliation: "1"
  - name: V.P. Nagraj
    affiliation: "1"
  - name: Matthew Scholz
    affiliation: "1"
  - name: Shakeel Jessa
    affiliation: "1"
  - name: Carlos Acevedo
    affiliation: "1"
  - name: Jianye Ge
    affiliation: "2,3"
  - name: August Woener
    affiliation: "2,3"
  - name: Bruce Budowle
    affiliation: "2,3"

>>>>

author:
  - name: Stephen D. Turner
    affiliation: "1"
  - name: V.P. Nagraj
    affiliation: "1"
  - name: Matthew Scholz
    affiliation: "1"
  - name: Shakeel Jessa
    affiliation: "1"
  - name: Carlos Acevedo
    affiliation: "1"
  - name: Jianye Ge
    affiliation: "2,3"
  - name: August Woerner
    affiliation: "2,3"
  - name: Bruce Budowle
    affiliation: "2,3"

### 2021-07-15 paper/paper.tex
typo

\author[FirstAuthorLastName \textit{et~al}.]{
Stephen D. Turner\,\textsuperscript{1}, V.P.
Nagraj\,\textsuperscript{1}, Matthew
Scholz\,\textsuperscript{1}, Shakeel Jessa\,\textsuperscript{1}, Carlos
Acevedo\,\textsuperscript{1}, Jianye Ge\,\textsuperscript{2,3}, August
Woener\,\textsuperscript{2,3}, Bruce Budowle\,\textsuperscript{2,3}
}

>>>>

\author[FirstAuthorLastName \textit{et~al}.]{
Stephen D. Turner\,\textsuperscript{1}, V.P.
Nagraj\,\textsuperscript{1}, Matthew
Scholz\,\textsuperscript{1}, Shakeel Jessa\,\textsuperscript{1}, Carlos
Acevedo\,\textsuperscript{1}, Jianye Ge\,\textsuperscript{2,3}, August
Woerner\,\textsuperscript{2,3}, Bruce Budowle\,\textsuperscript{2,3}
}
